19Q2

### 2019-06-13 19Q2.Rmd
figure out failed CTRP protein change heatmap

>>>>

```{r, eval=FALSE}
ctrp_signif_prot <- readRDS("./data_munging/rds/ctrp_signif_protein_changes.rds")
ctrp_signif_prot <- merge(ctrp_signif_prot, unique(select(ctrp_prot, Drug_Gene_Protein_Change, Direction_Curated)), by = "Drug_Gene_Protein_Change", all.x = TRUE)

signif_df <- ctrp_signif_prot

signif_grid <- dcast(signif_df, Gene_Protein_Change ~ Drug, value.var = "p_log10", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene_Protein_Change)
signif_grid <- signif_grid[, intersect(g2p_drug_order, colnames(signif_grid))]
signif_grid <- signif_grid[complete.cases(signif_grid), ]
signif_grid[signif_grid < -log10(0.05)] <- NA

signif_grid_annot <- dcast(signif_df, Gene_Protein_Change ~ Drug, value.var = "Direction_Curated", fill = 0)
%>% `rownames<-`(.[,1]) %>% select(-Gene_Protein_Change)
signif_grid_annot <- signif_grid_annot[, intersect(g2p_drug_order, colnames(signif_grid))]
signif_grid_annot <- signif_grid_annot[complete.cases(signif_grid_annot), ]
signif_grid_annot[signif_grid_annot == "No"] <- ""
signif_grid_annot[signif_grid_annot == "Yes"] <- "O"

test <- ctrp_signif_prot %>% count(Gene_Protein_Change, Drug)
```
